Simulating Dwarf Galaxy Evolution with Individual Star Feedback and Chemical Evolution

### 2018-02-16 main.tex
completed revision of sections 2 and 3.

%mm2 I think there does need to be some introduction to this discussion:
   However, the bulk of this work has been done with fully Lagrangian
%mm2 Fully Lagrangian schemes, like native 
smoothed particle hydrodynamics (SPH), 
%mm2 are incapable of capturing
    with a few recent exceptions  \citep{Few2012,Few2014,Vorobyov2015}. In its original form, 
    SPH cannot model
mixing between chemically inhomogeneous particles, as necessary for chemical evolution. This must be handled through sub-grid models of turbulent metal diffusion \citep[e.g.][]{Shen2010, Shen2013,Brook2014,Su2017a}. Even more, there are many possible sub-grid models that are not applicable in every regime \citep[see ][]{Revaz2016}, though recent studies have shown great improvements in characterizing various methods \citep{Escala2017}. While mixing occurs in Eulerian codes even without sub-grid models, numerical diffusion tends to result in over-mixing, requiring very high resolution or additional viscosity to reduce. Molecular diffusion %mm2 
    or even turbulent mixing
is certainly not resolved in any galaxy-scale simulation with either method, requiring additional sub-grid models; this can be particularly important for understanding the initial pollution of otherwise pristine gas \citep[see ][ and references therein]{PanScannapiecoScalo2013,Sarmento2017}. Moreover, metal mixing efficiencies may vary species-by-species, as suggested by recent work \citep[e.g.][]{Cohen2013, Roederer2014, FrebelNorris2015, Hirai2017, Cote2017}. Mixing behavior is tied critically to the feedback source (stellar winds, supernovae, and possibly more exotic sources) 
%mm in which they are injected to
    that inject metals into 
%mm2
    different phases of 
the ISM with different energies and on different timescales; the observational effect of this is poorly understood, however. The variations in how different methods handle sub-grid metal injection and metal mixing schemes can lead to uncertainties in connecting models to observations and the fundamental physics that drives galaxy evolution.
%mm2 [cited above] \textbf{Still not sure about this sentence - but I do need a way to cite mentioned papers:} Extending these models to a grid-based code is a valuable and complementary approach towards investigating galactic chemical evolution that has only been done recently \citep{Few2012,Few2014,Vorobyov2015}.

@@

%mm2 [if we were to keep the previous sentence, we'd need to segue like this.]
%   Nevertheless, we 
We introduce a new method for studying galactic chemical evolution that follows stars as individual star particles implemented in the adaptive mesh refinement code \texttt{Enzo}, designed for high resolution simulations of isolated galaxies. The relative simplicity of idealized, isolated galaxy evolution simulations allows for a focused, first-principles approach to studying multi-channel feedback mechanisms. We follow recent work using low mass dwarf galaxies as laboratories to study in detail how feedback governs galaxy evolution \citep{Forbes2016,Hu2016,Hu2017}.
%For example, \citet{Forbes2016} found that photoelectric heating can be a significant source of feedback in small galaxies. \citet{Hu2016} and \citet{Hu2017} examined the relative importance of various feedback physics in regulating ISM properties of dwarf galaxies. 
Our work builds upon our current understanding of feedback and galactic chemodynamics while making three notable advances: 1) direct star-by-star modeling, 2) stellar wind feedback from both massive and asymptotic giant branch (AGB) stars, and 3) using an adaptive ray tracing method to follow stellar ionizing radiation. 
%mm2
  We include stellar feedback from stellar winds, core collapse and Type Ia supernovae,    
  photoelectric heating, and ionizing radiation.

Using star-by-star modeling, we capture in more detail the stellar yields from individual stars released over their lifetime. self-consistent set of stellar yields. 
%mm2 
    We track yields from massive and AGB star winds, and supernovae. 
In addition to better capturing how individual metal species enrich the ISM, this allows us to chemically tag individual stars. This ability opens an exciting new channel for testing models of galaxy evolution by leveraging current and ongoing observations probing the detailed 
%mm2
   distributions of
chemical abundances of stars in the Milky Way and Local Group, such as APOGEE and APOGEE2 \citep{APOGEE2010,APOGEE}, the Gaia-ESO survey \citep{Gaia}, and GALAH \citep{GALAH}.
%mm2 
This paper is the first in a series examining in detail the role that the individual components of multi-channel stellar feedback play in galaxy dynamical and chemical evolution. 
%mm2 [this is somehow redundant with the previous paragraph.  I have moved a few things up.]
% In this paper we introduce a new method of feedback physics and galactic chemical enrichment in the cosmological, hydrodynamics code \texttt{Enzo}. For the first time in galaxy-scale simulations, we model star formation down to particles representing individual stars, while simultaneously capturing stellar feedback through stellar winds, core collapse and Type Ia supernovae, photoelectric heating, and ionizing radiation through ray-tracing radiative transfer. In addition, we couple to a self-consistent set of stellar yields
%to track yields from massive star stellar winds, AGB star winds, and supernovae. 
We describe each mode of our multi-channel feedback 
in detail in Sect.~\ref{sec:methods}, describe their implementation in an isolated dwarf galaxy simulation
%mm2 
   in Sect.~\ref{sec:IC}, show results from this simulation in Sect.~\ref{sec:results}, discuss the 
   results in Sect.~\ref{sec:discussion}, and conclude in Sect.~\ref{sec:conclusion}.

@@

\section{Methods}
\label{sec:methods}
%mm2 In  summary, 
We produce high-resolution, galaxy-scale simulations tracking stars not as SSP's, but as individual stars sampled from an assumed IMF.
This allows us to follow star-by-star variations in feedback physics and stellar yields in detail. To properly model the ISM, we track non-equilibrium, primordial chemistry (including molecular hydrogen) using \texttt{Grackle} \citep{GrackleMethod}, with heating and approximate self-shielding from a metagalactic ultraviolet (UV) background. We 
assume collisional ionization equilibrium for all other elements in order to
use updated \texttt{Cloudy} metal-line cooling tables consistent with our self-shielding approximation (see Appendix ~\ref{appendix:cooling}), and an updated observationally motivated dust model for the low metallicity regimes studied here ($Z \lesssim 0.1$ Z$_{\odot}$). Each star is assigned basic properties including surface gravity, effective temperature, radius, and lifetime from tabulated stellar evolution models, which inform how the stars deposit their feedback. We directly track ionizing radiation from massive stars using an adaptive ray tracing radiative transfer method that includes the effects of radiation pressure. In addition, we follow the optically thin, non-ionizing UV radiation from these stars leading to photoelectric heating and Lyman-Werner dissociation of molecular hydrogen. We track the stellar wind feedback and supernovae from these stars, depositing individual metal yields from both. We include AGB wind feedback and yields for lower mass stars, and track these directly as Type Ia supernova progenitors. We follow yields for 15 individual metal species (C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba), chemically tagging each star as it forms
with the associated local gas abundances for each species. In addition, we track a total metal density field which is the sum of all metals, including those not directly tracked. This field is used to inform the heating/cooling physics, and determines the metallicity of each star at birth. These methods are discussed in full detail below.

@@

\subsection{Star Formation Algorithm}
\label{sec:star formation}
In order to resolve individual star formation events on galaxy scales, we implement a stochastic star formation algorithm adopted from \citet{Goldbaum2015,Goldbaum2016}. Each cell at the maximum refinement level is capable of forming stars if it meets the following local criteria: 1) $n_{\rm cell} > n_{\rm thresh}$, 2) $T_{\rm gas} < T_{\rm thresh}$, 3) $M_{\rm gas} > M_{\rm Jeans}$, and 4) $\vec{\nabla} \cdot \vec{v} < 0$, where $n_{\rm thresh}$ is a resolution dependent density threshold, $T_{\rm thresh}$ is a temperature threshold, and $M_{\rm Jeans}$ is the local Jeans mass. Our fiducial values for $n_{\rm thresh}$ and $T_{\rm thresh}$ are 200~cm$^{-3}$ and 200~K respectively. We limit the fraction of a cell's gas mass that is converted into stars by requiring $M_{\rm gas} > f_{\rm thresh} M_{\rm max,*}$, where $f_{\rm thresh} = 2.0 $ and $M_{\rm max,*}$ is the maximum star mass (100 M$_{\odot}$). No star formation occurs when $M_{\rm gas} < f_{\rm thresh} M_{\rm max,*}$, ensuring that a star formation episode does not produce negative densities.

We make the common ansatz that star formation occurs by converting some fraction of gas into stars in a free fall time ($\tau_{\rm ff}$) as characterized by a star formation efficiency, $\epsilon_{\rm f} \simeq 0.02$. At high resolution, one's choice of $\epsilon_{\rm f}$ should be irrelevant \citep{Orr2017, FIRE2}, as star formation is ultimately self-regulated by feedback.
%but we find that $\epsilon_{\rm f}$ may impact star formation in the lowest mass halos, which are unusually sensitive to stellar ionization feedback (see Emerick et. al. in prep).
The gas mass converted to stars in a time step, $dt$, is
\begin{equation}
M_{ {\rm gas} \to *} = \epsilon_{\rm f} M_{\rm gas} \frac{dt}{\tau_{\rm ff}}.
\end{equation}
In practice, $dt/\tau_{\rm ff} \ll 1$, and $M_{ {\rm gas} \to *}$ is smaller than the minimum star particle mass at parsec scale resolution. We therefore allow star formation to proceed stochastically, following the methods in \citet{Goldbaum2015, Goldbaum2016}, modified for variable stellar masses. In each cell that could potentially form stars, we compute the probability that 100 M$_{\odot}$ of gas will be converted into stars in that time step, and use a random number draw to determine whether or not star formation actually occurs. If it does, we randomly sample over the adopted IMF until 100 M$_{\odot}$ of stars form, keeping the last sampled particle if the total stellar mass formed exceeds 100 M$_{\odot}$. We make the simple assumption of a Salpeter IMF \citep{Salpeter1955} with $\alpha = 2.35$, sampling over a minimum stellar mass of 1 M$_{\odot}$ and an arbitrarily chosen maximum stellar mass of 100 M$_{\odot}$. Our lower limit on stellar masses ensures that we are able to both directly track all particles that participate in some way to feedback and metal enrichment, and follow longer lived start particles, while reducing the computational expense of following many low mass stars that have no dynamical impact on the galaxy evolution.

Formed stars are deposited with random positions within the star forming cell and assigned velocities equal to the cell bulk velocity with a 1~km~s$^{-1}$ velocity dispersion. This dispersion captures some of the unresolved gas motions below the resolution limit and smoothed out by numerical diffusion; it is comparable to, but less than, the velocity dispersion of the coldest gas in our simulations. Stars are assigned metallicities corresponding to the metallicity of the star forming zone, and are chemically tagged with the 17 individual species abundances (H, He, and the 15 metals) that we follow in our simulations. Stars evolve during the simulation, by losing mass from stellar winds and supernovae as described below, and by changing types, but persist throughout the entire simulation. For example, low mass stars are tagged as white dwarfs at the end of their life, which may eventually explode as a Type Ia supernova (discussed below), after which they persist as massless tracer particle ``remnants''.

Finally, each star is marked as a ``must refine" particle, requiring that each star be surrounded by a four-cell region at the highest level of refinement. This ensures that both stellar winds and supernovae feedback are maximally resolved, and that any ejected yields are deposited over a consistent physical scale throughout the simulation.

@@

\subsubsection{Stellar Yields}
\label{sec:yields}
For the first time in galaxy scale simulations, we track galactic chemodynamical evolution using stellar yields as ejected from star particles that represent individual stars. We adopt the NuGrid\footnote{http://www.nugridstars.org} collaboration's set of stellar yields given on a uniformly sampled grid in stellar mass and metallicity with 12 mass bins over $M_{*} \in \left[1.0, 25.0\right]$ M$_{\odot}$ and five metallicity bins at $Z =$ 0.02, 0.01, 0.006, 0.001, and 10$^{-4}$ \citep{Pignatari2016, Ritter2017}. This grid includes yields from the AGB phase of stars between 1 and 7 M$_{\odot}$, as well as yields from both stellar winds and core collapse supernova of massive stars over 12 to 25 M$_{\odot}$. We complement these tables with tables from Slemer et. al. (in prep), based on the PARSEC stellar evolution tracks \citep{Bressan2012, Tang2014} to track stellar winds for stars more massive than 25 M$_{\odot}$. We ignore supernova yields from these stars (see next paragraph). We combine all stable isotope yields for a given element into a single elemental abundance for all stable elements from hydrogen to bismuth. Although we can follow an arbitrary number of metal species, practical considerations of memory use prevent this in any given simulation. We refer the reader to previous uses of the NuGrid yields in one-zone galactic chemical enrichment models \citep{Cote2016,  Cote2016_feb,Cote2017} for a detailed discussion of how various model uncertainties can influence galactic chemical evolution.

Above some mass $M_{\rm trans}$ within the unsampled range of 7--12 M$_{\odot}$, stars do not undergo AGB wind phases and end their lives as core collapse supernovae. Where this transition occurs is uncertain, but is commonly taken to be around 8--10~M$_{\odot}$. This is a free parameter in our model, but we take $M_{\rm trans} = 8$~M$_{\odot}$ as our fiducial value. In our model, stars below this mass eject their wind yields in an AGB phase only at the end of their lives, typically over a period comparable to or less than a few time steps ($\lesssim 10$ kyr). Stars above this mass are assumed to eject their stellar yields via line-driven stellar winds at a constant mass loss rate throughout their lifetime (neglecting Wolf-Rayet and luminous blue variable phases), ending their lives as a core-collapse supernova (see Section \ref{sec:stellar winds} for details on the wind energetics). Varying $M_{\rm thresh}$ changes both the time at which yields for stars around this mass are ejected (for reference, the lifetime of a 8 M$_{\odot}$ star is about 35--40~Myr), and the energy injection from these winds. \citet{Cote2017} explores how the choice of $M_{\rm thresh}$ affects galaxy abundances in a one-zone model. We neglect the effects of binary star evolution on stellar feedback, but discuss the significance of this in Section~\ref{sec:binary stars}.

There are large uncertainties in stellar yields for stars more massive than 25 M$_{\odot}$ \citep[see ][and references therein]{Cote2016}. Indeed, even the exact fate of these stars is uncertain \citep[e.g.][]{Woosley2002,Zhang2008,Ugliano2012}, particularly as a function of metallicity \citep{Fryer2012} with potentially multiple stable and unstable regimes as a function of mass \citep{Heger2003}. Due to this uncertainty, and to avoid erroneously extrapolating from our yield tables, we adopt the simplest model and assume all stars above 25 M$_{\odot}$ end their life through direct collapse to a compact object with no further mass or energy ejection.

Type Ia supernovae are an important additional source of galactic chemical enrichment. These iron group rich events are responsible for the $\sim$1 Gyr timescale turnover, or ``knee", in $[\alpha/\rm{Fe}]$ vs $[\rm{Fe}/\rm{H}]$ diagrams. We use the Type Ia supernova yields given in \citet{Thielemann1986}, adopting a Type Ia supernova model as discussed in Section~\ref{sec:Type Ia}. We emphasize that we only track Type Ia supernovae occurring within the population of stars formed in this model, neglecting supernovae from any pre-existing population.

\subsubsection{Stellar Winds}
\label{sec:stellar winds}
Stellar winds are important sources of enrichment and feedback in galaxies at both early times from massive stars and late times from AGB stars. Although the energy injected via winds over the lifetime of a cluster of stars is much less than that from supernovae and radiation, stellar winds are potentially important sources of pre-supernova feedback. In models that include feedback energy from stellar winds from both AGB and  massive stars, we inject the feedback energy in a three-cell radius spherical region centered on the emitting star particle, assuming full thermalization of the wind kinetic energy. The total injected energy in timestep $\Delta t$ is therefore $E_{\rm wind} = \dot{M}\Delta t \times v^2_{\rm wind} + E_{\rm th}$, where $E_{\rm th}$ is the thermal energy of the ejected gas mass ($\dot{M}\Delta t$) given the star's interpolated $T_{\rm eff}$. We use a Monte Carlo sampling method to inject mass and energy into the surrounding cells to account for partial cell overlap at the edge of the injection region that is a result of mapping a spherical injection region to cubic grid cells.

We assume constant mass loss rates for all winds as set by the yields tables over either the lifetime of the star (for massive stars) or the length of the AGB phase (for low mass stars). 
%Properly modeling stellar winds requires sub-parsec resolution, which is problematic in galaxy-scale simulations.

Massive stellar winds have typical velocities of order 10$^{3}$ km s$^{-1}$ \citep{Leitherer1992}. Satisfying the Courant time step becomes prohibitively expensive following this gas ($dt \sim$~100~yr), particularly as stellar wind bubbles have typical temperatures of 2 $\times$ 10$^{6}$ K \citep{Weaver1977}. For this reason, we adopt the common simplification of reducing the wind velocity \citep[e.g][]{Offner2015}. In our case, we fix massive stellar winds to $v_{\rm wind} = 1$~km~s$^{-1}$ for stars above 8 M$_{\odot}$. Our initial tests show that turning off energy injection from stellar winds like this does not significantly affect the global star formation rate of our galaxies. Due to the substantial additional computational expense of following stellar winds for gigayear timescales, we reserve examining the detailed importance of winds to future work. These points are discussed in more detail in Section \ref{sec:stellar winds discussion}.

@@

\textbf{In response to MM's comment: I focus on G$_o$ here because I found it to be the more general quantity, getting at how one should think of / model the time-and-space-varying ISFR in a tiny dwarf galaxy (i.e. how does this compare to a uniform or 1D radial profile). G$_{eff}$ is convolved with local density and temperature variations, and is thus a bit harder to parse / interpret. Though possibly I should show both?}

@@

\section{Typical Gas Densities in Supernova Injection Regions}
\label{appendix:supernova}

>>>>

%mm2 I think there does need to be some introduction to this discussion:
   However, the bulk of this work has been done with fully Lagrangian
%mm2 Fully Lagrangian schemes, like native 
smoothed particle hydrodynamics (SPH), 
%mm2 are incapable of capturing
    with a few recent exceptions  \citep{Few2012,Few2014,Vorobyov2015}. In its original form, 
    SPH cannot model
mixing between chemically inhomogeneous particles, as necessary for chemical evolution. This must be handled through sub-grid models of turbulent metal diffusion \citep[e.g.][]{Shen2010, Shen2013,Brook2014,Su2017a}. Even more, there are many possible sub-grid models that are not applicable in every regime \citep[see ][]{Revaz2016}, though recent studies have shown great improvements in characterizing various methods \citep{Escala2017}. While mixing occurs in Eulerian codes even without sub-grid models, numerical diffusion tends to result in over-mixing, requiring very high resolution or additional viscosity to reduce. Molecular diffusion %mm2 
    or even turbulent mixing
is certainly not resolved in any galaxy-scale simulation with either method, requiring additional sub-grid models; this can be particularly important for understanding the initial pollution of otherwise pristine gas \citep[see ][ and references therein]{PanScannapiecoScalo2013,Sarmento2017}. Moreover, metal mixing efficiencies may vary species-by-species, as suggested by recent work \citep[e.g.][]{Cohen2013, Roederer2014, FrebelNorris2015, Hirai2017, Cote2017}. Mixing behavior is tied critically to the feedback source (stellar winds, supernovae (SNe), and possibly more exotic sources) 
%mm in which they are injected to
    that inject metals into 
%mm2
    different phases of 
the ISM with different energies and on different timescales; the observational effect of this is poorly understood, however. The variations in how different methods handle sub-grid metal injection and metal mixing schemes can lead to uncertainties in connecting models to observations and the fundamental physics that drives galaxy evolution.
%mm2 [cited above] \textbf{Still not sure about this sentence - but I do need a way to cite mentioned papers:} Extending these models to a grid-based code is a valuable and complementary approach towards investigating galactic chemical evolution that has only been done recently \citep{Few2012,Few2014,Vorobyov2015}.

@@

%mm2 [if we were to keep the previous sentence, we'd need to segue like this.]
%   Nevertheless, we 
We introduce a new method for studying galactic chemical evolution that follows stars as individual star particles implemented in the adaptive mesh refinement code \texttt{Enzo}, designed for high resolution simulations of isolated galaxies. The relative simplicity of idealized, isolated galaxy evolution simulations allows for a focused, first-principles approach to studying multi-channel feedback mechanisms. We follow recent work using low mass dwarf galaxies as laboratories to study in detail how feedback governs galaxy evolution \citep{Forbes2016,Hu2016,Hu2017}.
%For example, \citet{Forbes2016} found that photoelectric heating can be a significant source of feedback in small galaxies. \citet{Hu2016} and \citet{Hu2017} examined the relative importance of various feedback physics in regulating ISM properties of dwarf galaxies. 
Our work builds upon our current understanding of feedback and galactic chemodynamics while making three notable advances: 1) direct star-by-star modeling, 2) stellar wind feedback from both massive and asymptotic giant branch (AGB) stars, and 3) using an adaptive ray tracing method to follow stellar ionizing radiation. 
%mm2
  We include stellar feedback from stellar winds, core collapse and Type Ia SNe,    
  photoelectric heating, and ionizing radiation.

Using star-by-star modeling, we capture in more detail the stellar yields from individual stars released over their lifetime. self-consistent set of stellar yields. 
%mm2 
    We track yields from massive and AGB star winds, and SNe. 
In addition to better capturing how individual metal species enrich the ISM, this allows us to chemically tag individual stars. This ability opens an exciting new channel for testing models of galaxy evolution by leveraging current and ongoing observations probing the detailed 
%mm2
   distributions of
chemical abundances of stars in the Milky Way and Local Group, such as APOGEE and APOGEE2 \citep{APOGEE2010,APOGEE}, the Gaia-ESO survey \citep{Gaia}, and GALAH \citep{GALAH}.
%mm2 
This paper is the first in a series examining in detail the role that the individual components of multi-channel stellar feedback play in galaxy dynamical and chemical evolution. 
%mm2 [this is somehow redundant with the previous paragraph.  I have moved a few things up.]
% In this paper we introduce a new method of feedback physics and galactic chemical enrichment in the cosmological, hydrodynamics code \texttt{Enzo}. For the first time in galaxy-scale simulations, we model star formation down to particles representing individual stars, while simultaneously capturing stellar feedback through stellar winds, core collapse and Type Ia SNe, photoelectric heating, and ionizing radiation through ray-tracing radiative transfer. In addition, we couple to a self-consistent set of stellar yields
%to track yields from massive star stellar winds, AGB star winds, and SNe. 
We describe each mode of our multi-channel feedback 
in detail in Sect.~\ref{sec:methods}, describe their implementation in an isolated dwarf galaxy simulation
%mm2 
   in Sect.~\ref{sec:IC}, show results from this simulation in Sect.~\ref{sec:results}, discuss the 
   results in Sect.~\ref{sec:discussion}, and conclude in Sect.~\ref{sec:conclusion}.

@@

\section{Methods}
\label{sec:methods}
%mm2 In  summary, 
We produce high-resolution, galaxy-scale simulations tracking stars not as SSPs, but as individual stars sampled from an assumed IMF.
This allows us to follow star-by-star variations in feedback physics and stellar yields in detail. To properly model the ISM, we track non-equilibrium, primordial chemistry (including molecular hydrogen) using \texttt{Grackle} \citep{GrackleMethod}, with heating and approximate self-shielding from a metagalactic ultraviolet (UV) background. We 
assume collisional ionization equilibrium for all other elements in order to
use updated \texttt{Cloudy} metal-line cooling tables consistent with our self-shielding approximation (see Appendix ~\ref{appendix:cooling}), and an updated observationally motivated dust model for the low metallicity regimes studied here ($Z \lesssim 0.1$ Z$_{\odot}$). Each star is assigned basic properties including surface gravity, effective temperature, radius, and lifetime from tabulated stellar evolution models, which inform how the stars deposit their feedback. We directly track ionizing radiation from massive stars using an adaptive ray tracing radiative transfer method that includes the effects of radiation pressure. In addition, we follow the optically thin, non-ionizing UV radiation from these stars leading to photoelectric heating and Lyman-Werner dissociation of molecular hydrogen. We track the stellar wind feedback and SNe from these stars, depositing individual metal yields from both. We include AGB wind feedback and yields for lower mass stars, and track these directly as Type Ia SN progenitors. We follow yields for 15 individual metal species (C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba), chemically tagging each star as it forms
with the associated local gas abundances for each species. In addition, we track a total metal density field which is the sum of all metals, including those not directly tracked. This field is used to inform the heating/cooling physics, and determines the metallicity of each star at birth. These methods are discussed in full detail below.

@@

\subsection{Star Formation Algorithm}
\label{sec:star formation}
In order to resolve individual star formation events on galaxy scales, we implement a stochastic star formation algorithm adopted from \citet{Goldbaum2015,Goldbaum2016}. Each cell at the maximum refinement level is capable of forming stars if it 
%mm2 
   contains gas that 
meets the following local criteria
%mm2 [removed extraneous subscripts and simplified a bit]
     on number density $n$, temperature $T$, cell mass $M$, and velocity $\vec{v}$:
1) $n > n_{\rm thresh}$, 2) $T < T_{\rm thresh}$, 3) $M > M_{\rm Jeans}$, and 4) $\vec{\nabla} \cdot \vec{v} < 0$, where $n_{\rm thresh}$ is a resolution dependent density threshold, $T_{\rm thresh}$ is a temperature threshold, and $M_{\rm Jeans}$ is the local Jeans mass. Our fiducial values are $n_{\rm thresh} =  200 \mbox{ cm}^{-3}$ and $T_{\rm thresh}= 200$~K. We limit the fraction of a cell's gas mass that is converted into stars by requiring $M > f_{\rm thresh} M_{\rm max,*}$, where $f_{\rm thresh} = 2.0 $ and the maximum star mass $M_{\rm max,*} = 100 \mbox{ M}_{\odot}$. No star formation occurs when $M < f_{\rm thresh} M_{\rm max,*}$, ensuring that a star formation episode can not produce negative densities.

We make the common ansatz that star formation occurs by converting some fraction of gas into stars in a free fall time ($\tau_{\rm ff}$) as characterized by a star formation efficiency, $\epsilon_{\rm f} \simeq 0.02$. At high resolution, one's choice of $\epsilon_{\rm f}$ should be irrelevant \citep{Orr2017, FIRE2}, as star formation is ultimately self-regulated by feedback.
%but we find that $\epsilon_{\rm f}$ may impact star formation in the lowest mass halos, which are unusually sensitive to stellar ionization feedback (see Emerick et. al. in prep).

%mm2 The gas mass converted to stars in a time step, $dt$, is
   The stellar mass formed during a timestep $\Delta t$ is
\begin{equation}
%mm2 M_{ {\rm gas} \to *} = \epsilon_{\rm f} M_{\rm gas} \frac{dt}{\tau_{\rm ff}}.
         M_* = \epsilon_{\rm f} M_{\rm gas} \frac{\Delta t}{\tau_{\rm ff}}
\end{equation}
In practice, $\Delta t/\tau_{\rm ff} \ll 1$, and $M_*$ is smaller than the minimum star particle mass at parsec scale resolution. We therefore allow star formation to proceed stochastically, following the methods in \citet{Goldbaum2015, Goldbaum2016}, modified for variable stellar masses. In each cell that could potentially form stars, we compute the probability that 100 M$_{\odot}$ of gas will be converted into stars in that time step, and use a random number draw to determine whether or not star formation actually occurs. If it does, we randomly sample 
%mm2 over 
   from
the adopted IMF until 100 M$_{\odot}$ of stars form, keeping the last sampled particle 
%mm2 if 
   when 
the total stellar mass formed exceeds 100 M$_{\odot}$. We 
%mm2 make the simple assumption of 
     assume 
a Salpeter IMF \citep{Salpeter1955} with $\alpha = 2.35$, sampling over
%mm2
   the range between  
a minimum stellar mass of 1 M$_{\odot}$ and an arbitrarily chosen maximum stellar mass of 100 M$_{\odot}$. Our lower limit on stellar masses ensures that we are able to both directly track all particles that contribute in some way to feedback and metal enrichment, and follow longer lived star particles, while reducing the computational expense of following a large number of low mass stars that have no dynamical impact on the galaxy evolution.

Formed stars are deposited with random positions within the star forming cell and assigned velocities equal to the cell bulk velocity with a 1~km~s$^{-1}$ velocity dispersion. This dispersion captures some of the unresolved gas motions below the resolution limit that are smoothed out by numerical diffusion; it is comparable to, but less than, the velocity dispersion of the coldest gas in our simulations. Stars are assigned metallicities corresponding to the metallicity of the star forming zone, and are chemically tagged with the 17 individual species abundances (H, He, and the 15 metals) that we follow in our simulations.

%mm2 [moved para break up]
Stars evolve during the simulation, by losing mass from stellar winds and SNe as described below, and by changing types, but persist throughout the entire simulation. For example, low mass stars are tagged as white dwarfs (WDs) at the end of their life, which may eventually explode as a Type Ia SN (discussed below), after which they persist as massless tracer particle remnants. Finally, each star is marked as a ``must refine'' particle, requiring that it be surrounded by a four-cell region at the highest level of refinement. This ensures that both stellar winds and SNe feedback are maximally resolved, and that any ejected yields are deposited over a consistent physical scale throughout the simulation.

@@

\subsubsection{Stellar Yields}
\label{sec:yields}
For the first time in galaxy scale simulations, we track galactic chemodynamical evolution using stellar yields as ejected from star particles that represent individual stars. We adopt the NuGrid\footnote{http://www.nugridstars.org} collaboration's set of stellar yields given on a uniformly sampled grid in stellar mass and metallicity with 12 mass bins over $M_{*} \in \left[1.0, 25.0\right]$ M$_{\odot}$ and five metallicity bins at $Z =$ 0.02, 0.01, 0.006, 0.001, and 10$^{-4}$ \citep{Pignatari2016, Ritter2017}. This grid includes yields from the AGB phase of stars from 1--7 M$_{\odot}$, as well as yields from both stellar winds and core collapse SNe of massive stars from 12--25 M$_{\odot}$. We complement these tables with tables from Slemer et. al. (in prep), based on the PARSEC stellar evolution tracks \citep{Bressan2012, Tang2014} to track stellar winds for stars more massive than 25 M$_{\odot}$. We ignore SN yields from these stars (see next paragraph). We combine all stable isotope yields for a given element into a single elemental abundance for all stable elements from hydrogen to bismuth. Although we can in principle follow an arbitrary number of metal species, practical considerations of memory use prevent this in any given simulation. We refer the reader to previous uses of the NuGrid yields in one-zone galactic chemical enrichment models \citep{Cote2016,  Cote2016_feb,Cote2017} for a detailed discussion of how various model uncertainties can influence galactic chemical evolution.

Above some mass $M_{\rm trans}$ within the unsampled range of 7--12 M$_{\odot}$, stars do not undergo AGB wind phases and end their lives as core collapse SNe. Where this transition occurs is uncertain, but is commonly taken to be around 8--10~M$_{\odot}$. This is a free parameter in our model, but we take $M_{\rm trans} = 8$~M$_{\odot}$ as our fiducial value. In our model, stars below this mass eject their wind yields in an AGB phase only at the end of their lives, typically over a period comparable to or less than a few time steps ($\lesssim 10$ kyr). Stars above this mass are assumed to eject their stellar yields via line-driven stellar winds at a constant mass loss rate throughout their lifetime (neglecting Wolf-Rayet and luminous blue variable phases), ending their lives as a core-collapse SN (see Sect.~\ref{sec:stellar winds} for details on the wind energetics). Varying $M_{\rm thresh}$ changes both the time at which yields for stars around this mass are ejected (for reference, the lifetime of an 8 M$_{\odot}$ star is about 35--40~Myr), and the energy injection from these winds. \citet{Cote2017} explores how the choice of $M_{\rm thresh}$ affects galaxy abundances in a one-zone model. We neglect the effects of binary star evolution on stellar feedback, and discuss the significance of this in Sect.~\ref{sec:binary stars}.

There are large uncertainties in stellar yields for stars more massive than 25 M$_{\odot}$ \citep[see ][and references therein]{Cote2016}. Indeed, even the exact fate of these stars is uncertain \citep[e.g.][]{Woosley2002,Zhang2008,Ugliano2012}, particularly as a function of metallicity \citep{Fryer2012} with potentially multiple stable and unstable regimes as a function of mass \citep{Heger2003}. Due to this uncertainty, and to avoid erroneously extrapolating from our yield tables, we adopt the simplest model and assume all stars above 25 M$_{\odot}$ end their life through direct collapse to a compact object with no further mass, 
%mm2 
   metal, 
or energy ejection.

Type Ia SNe are an important additional source of galactic chemical enrichment. These iron group rich events are responsible for the $\sim$1 Gyr timescale turnover, or ``knee", in $[\alpha/\rm{Fe}]$ vs $[\rm{Fe}/\rm{H}]$ diagrams. We use the Type Ia SN yields given in \citet{Thielemann1986}, adopting a Type Ia SN model as discussed in Sect.~\ref{sec:Type Ia}. We emphasize that we only track Type Ia SNe occurring within the population of stars formed in this model, neglecting SNe from any pre-existing population.

\subsubsection{Stellar Winds}
\label{sec:stellar winds}
Stellar winds are important sources of enrichment and feedback in galaxies at both early times from massive stars and late times from AGB stars. Although the energy injected via winds over the lifetime of a cluster of stars is much less than that from SNe and radiation \citep{shull1995}, stellar winds are potentially important sources of pre-SN feedback. In models that include feedback energy from stellar winds from both AGB and massive stars, we inject the feedback energy in a three-cell radius spherical region centered on the emitting star particle, assuming full thermalization of the wind kinetic energy. The total injected energy in timestep $\Delta t$ is therefore $E_w = \dot{M}\Delta t \times v^2_w + E_{\rm th}$, where $E_{\rm th}$ is the thermal energy of the ejected gas mass $M_w = \dot{M}\Delta t$ given the star's interpolated effective temperature $T_{\rm eff}$. We use a Monte Carlo sampling method to inject mass and energy into the surrounding cells to account for partial cell overlap at the edge of the injection region that is a result of mapping a spherical injection region to cubic grid cells. We assume constant mass loss rates for all winds as set by the yield tables over either the lifetime of the star (for massive stars) or the length of the AGB phase (for low mass stars). 
%Properly modeling stellar winds requires sub-parsec resolution, which is problematic in galaxy-scale simulations.

Massive stellar winds have typical velocities of order 10$^{3}$ km s$^{-1}$ \citep{Leitherer1992}. Satisfying the Courant time step becomes prohibitively expensive following this gas, with time steps dropping to $\Delta t \sim$~100~yr.
%mm2 , particularly as stellar wind bubbles have typical temperatures of 2 $\times$ 10$^{6}$ K \citep{Weaver1977}.   [This yields a sound speed on the same order as the flow velocity, more or less by energy conservation, so doesn't change the timestep.]
For this reason, we adopt the common simplification of reducing the wind velocity \citep[e.g][]{Offner2015}. In our case, we fix massive stellar wind velocities to $v_w = 1$~km~s$^{-1}$ for stars above 8 M$_{\odot}$. Our initial tests show that turning off energy injection from stellar winds like this does not significantly affect the global star formation rate of our galaxies. Due to the substantial additional computational expense of following stellar winds for gigayear timescales, we reserve examining the detailed importance of winds to future work. These points are discussed in more detail in Sect.~\ref{sec:stellar winds discussion}.

@@

%mm2 \textbf{In response to MM's comment: I focus on G$_o$ here because I found it to be the more general quantity, getting at how one should think of / model the time-and-space-varying ISFR in a tiny dwarf galaxy (i.e. how does this compare to a uniform or 1D radial profile). G$_{eff}$ is convolved with local density and temperature variations, and is thus a bit harder to parse / interpret. Though possibly I should show both?  
%MM: given how low the optical depth is, it probably doesn't matter.}

@@

\section{Typical Gas Densities in SN Injection Regions}
\label{appendix:SN}
